### 2019-10-10 paper/abstract.tex
Andrei's comments impelemented Abstract & introduction

\begin{abstract}
Liquid-fueled Molten Salt Reactor (MSR) systems represent advances in safety, economics, sustainability, and proliferation-resistance. Therefore, \gls{MSR} has been selected as one of the promising reactors by the \gls{GIF}. Basically, the \gls{MSR} has been designed to operate based on Th/$^{233}$U fuel cycle. Since $^{233}$U does not exist in nature, it is required to examine available fissile materials to replace the $^{233}$U in the startup fuel. Here, five different types of initial fissile materials are proposed for transitioning to thorium fuel cycle in the \gls{SD-TMSR}. Plutonium mixed with \gls{LEU} (19.79\%), \gls{LEU} (19.79\%), Plutonium reactor-grade, \gls{TRU} from LWR spent fuel (SF) and finally $^{233}$U for comparison purpose are investigated. In the present paper, two different feed mechanisms are applied. Consequently, the multiplication factor, inventories of important nuclides and net production of $^{233}$U are studied. Moreover, the molten salt Temperature Coefficient of Reactivity $(\alpha$$_{T}$) is negative for startup and equilibrium states. The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel. Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U. 
\end{abstract}

@@

>>>>

\begin{abstract}
Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance. The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as start-up fissile material. Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials. This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at start-up: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} spent fuel with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}. The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work. The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for $^{233}$U start-up fuel. Finally, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
\end{abstract}

@@

%Therefore, \gls{MSR} has been selected as one of the promising reactors by the \gls{GIF}.

### 2019-10-10 paper/introduction.tex
Andrei's comments impelemented Abstract & introduction

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation 
nuclear systems. These goals are: safety and reliability, economics, 
sustainability, non-proliferation and physical protection 
\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent 
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online 
reprocessing and refueling, excellent neutron economy and near atmospheric 
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}. 
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV 
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl). 
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly 
circulates through the core and allows transferring fission heat from reactor 
core to heat exchanger.

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 
MW$_{th}$) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The 
SD-TMSR 
is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U 
fuel cycle. In the SD-TMSR the fissile and fertile elements are integrated 
into the same salt. In addition, the active core is divided into two zones, 
the radius of the fuel channels in the outer zone is modified to be larger 
than the radius of the fuel channels in the inner zone to improve the breeding 
ratio \cite{nuttin2005potential,li_optimization_2018}.

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U 
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
merle2004scenarios,rosenthal1970molten}. This design assumes that we have 
fissile $^{233}$U inventory to startup new \glspl{MSR}. But $^{233}$U does not 
exist in the Earth's crust and can be produced from fertile $^{232}$Th only in 
the nuclear reactor. Therefore, it is required to examine alternative fissile 
materials (e.g., $^{235}$U) to replace the $^{233}$U in the startup fuel 
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel 
cycle transition can be achieved after reaching the doubling 
time\footnote{Time required to produce enough amount of $^{233}$U to trigger a 
new SD-TMSR.} of $^{233}$U because in this case all startup fissile material 
is being substituted by newly produced $^{233}$U.

Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit 
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial 
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SF is the best alternative source 
to $^{233}$U because it has the highest ratio of fissile isotopes 
\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for 
the thorium fuel cycle transition in \gls{TMSR}: in-core transition and 
ex-core transition. Historically, the TMSR is launched with existing fissile 
material and thorium as a fertile material; then the $^{233}$U bred from 
thorium is rerouted into the core to maintain criticality. In contrast, the 
new approaches tends to store produced $^{233}$U out of the core until there 
is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel 
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU} 
as startup fuel. They concluded that the transition to thorium fuel cycle can 
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.
Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR} 
under different launching scenarios (e.g., enriched uranium and TRU) 
\cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the 
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these 
researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling, 
ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019, 
heuer2014towards,fiorina2013investigation}, while little focus on 
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary, 
zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other 
fissile materials (except $^{233}$U) was not studied before. Therefore, 
the main object of the present paper is to discuss the simulation of the 
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with 
different initial fissile materials and without any external feed of $^{233}$U 
to achieve the thorium fuel cycle transition. We investigated five different  
initial fissile materials: \gls{LEU}, Pu, and \gls{TRU} from LWR SF 
\cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
\begin{itemize}
	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}
This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2. Methodology and tools is descried in section 3. Extraction and feed mechanisms are addressed in section 4. Section 5 focuses on the results and discussion. Finally, section 6 highlights the conclusions.

>>>>

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation nuclear systems. These goals have been defined in four broad areas: safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}. \glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}. Therefore, in 2002 the \gls{MSR} has been chosen as one of the promising reactors by this forum \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel supposed to be in the form of liquid dissolved in molten salt (e.g., LiF or NaCl). This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly circulates through the core and allows transferring fission heat.

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 MWth) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The SD-TMSR is a graphite-moderated thermal-spectrum MSR. In the SD-TMSR the fissile and fertile elements are integrated into the same salt. In addition, the active core is divided into two zones, the radius of the fuel channels in the outer zone is modified to be larger than the radius of the fuel channels in the inner zone to improve the breeding ratio \cite{nuttin2005potential,li_optimization_2018}.

Basically, the \gls{MSR} has been designed to apply the Th/$^{233}$U fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,merle2004scenarios,rosenthal1970molten}. Hence, the fertile isotope $^{232}$Th is converted to the fissile isotope $^{233}$U, an isotope that is not exist in nature. Therefore it is required to examine available fissile materials (e.g., $^{235}$U and Pu) to replace the $^{233}$U in the startup fuel \cite{betzler2016modeling,zou2018transition}. The thorium fuel cycle transition can be achieved after reaching the doubling time\footnote{Time required to produce enough amount of $^{233}$U to trigger a new SD-TMSR.} of $^{233}$U.

Betzler, et al. discussed the simulation of the start-up of a MSBR unit cell with LEU (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial fissile materials \cite{betzler2016modeling}. They concluded that the plutonium vector extracted from LWR SF serves as the best alternative source to $^{233}$U thanks to the highest ratio of fissile isotopes \cite{betzler2016modeling}. Zou, et al. introduced two approaches for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition. In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality. In contrast, the latter way tends to store the bred $^{233}$U out of the core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Meanwhile, Zou, et al. studied the transitioning to thorium fuel cycle in a small modular Th-based molten salt reactor (smTMSR) using TRUs as startup fuel. They concluded that the transition to thorium fuel cycle can be achieved in thermal smTMSR with a proper fuel fraction \cite{zou2018preliminary}.
Heuer, et al., discussed the transition characteristics of the \gls{MSFR} under different launching scenarios (e.g., enriched uranium and TRU), they concluded that starting the Thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the MSRs with fissile materials alternative to $^{233}$U. Many of these researches focus on the fast-spectrum MSRs \cite{ashraf2019modeling,ashraf2018nuclear,heuer2014towards,fiorina2013investigation}, while little focus on thermal-spectrum MSRs \cite{betzler2016modeling,zou2018preliminary,zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature. Therefore, the main object of the present paper is to discuss the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition. To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed mechanisms are used as follows:

\begin{itemize}
	\item Continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}

All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30. We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling. SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}. Additionally, SERPENT-2 allows us to conduct the burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.

This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2. Methodology and tools is descried in section 3. Extraction and feed mechanisms are addressed in section 4. Section 5 focuses on the results and discussion. Finally, section 6 highlights the conclusions.

### 2019-10-10 paper/methods.tex
Andrei's comments impelemented Abstract & introduction

As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced matrix exponential solution based on the Chebyshev Rational Approximation Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time. This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the \texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}. Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, \texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the isotopes during reactor operation \cite{aufiero2013extended}. The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle. Then, this mass is added to the core at the beginning of the cycle by a certain flow rate.

>>>>

As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced matrix exponential solution based on the Chebyshev Rational Approximation Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time. This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the \texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}. Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, \texttt{pa-decay tank}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the isotopes during reactor operation \cite{aufiero2013extended}. The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle. Then, this mass is added to the core at the beginning of the cycle by a certain flow rate.
